\item The Student Government Communications Committee shall be a standing committee of the Student Senate and the Executive
Board. It shall be responsible for promoting the initiatives and activities of the Student Senate and Executive Board.
\begin{enumerate}
\item Its chair shall meet with the Grand Marshal, the President of the Union, or their representatives at least twice a month to maintain cohesion and communication between their respective bodies.
\item Its chair may act as the spokesperson for the Senate and Executive Board at the discretion of the Grand Marshal and the President of the Union, responsible for press releases and other communication with media outlets.
\item Its membership shall include at least one member of the Senate, at least one member of the Executive Board, and the Vice
Chairs of the following Senate Committees:
\begin{enumerate}
\item Academic Affairs Committee,
\item Facilities and Services Committee,
\item Hospitality Services Advisory Committee, and
\item Student Life Committee,
\item However, if any of these committees do not have a Vice Chair appointed, the committee's chair shall fill the membership requirement themselves.
\end{enumerate}
\item It shall make use of a variety of communication media to publicize the initiatives and activities of the Senate and the
Executive Board.
\begin{enumerate}
\item To this end, it shall coordinate with other Senate Committees to promote current projects and initiatives.
\item It shall provide the student body with accurate information on the activities, initiatives, and projects of the Senate.
\end{enumerate}
\item It shall make efforts to ascertain the concerns of students, and the opinions of students regarding matters under discussion
in the Senate and the Executive Board.
\begin{enumerate}
\item It may solicit student concerns and opinions through public relations initiatives.
\item It shall inform other Committees of student concerns pertaining to the purview of each Committee.
\end{enumerate}

\item It shall foster, among the student body, informed discussion of issues currently facing the Senate and the Executive Board.
\begin{enumerate}
\item It shall, when necessary, create and distribute informational media in conjunction with its ongoing public relations
initiatives.
\item It shall create and maintain platforms for student inquiry into the activities of the Senate and the Executive Board.
\item It may coordinate publication of electronic media with the Web Technologies Committee when necessary.
\item It shall attempt to create an open dialogue between the student body and the Institute Administration through meetings
and public relations events.
\end{enumerate}

\item It shall promote cohesion among members and Committees of the Senate and the Executive Board.
\begin{enumerate}
\item To this end, it shall promote and facilitate internal communications of the Senate and the Executive Board.
\end{enumerate}
\end{enumerate}
