\item The Student Life Committee shall be responsible for initiatives and legislation pertinent to student rights, residence life,
quality of life and well-being, and the Office of Student Life portfolio.
\begin{enumerate}
\item It shall take steps to gather information on the state of residence life, quality of life, and well-being.
\begin{enumerate}
\item To this end, it shall coordinate with the Student Government Communications Committee during outreach programs to
ascertain student opinions and concerns within these areas.
\item It shall, from time to time, inspect the state of the Residence Halls and report its findings to the Senate.
\end{enumerate}
\item It shall address issues pertaining to student rights and responsibilities as they arise.
\begin{enumerate}
\item It shall work with the Dean of Students to discuss pending changes to the Handbook of Student Rights and
Responsibilities, or other relevant policies that affect student rights.
\end{enumerate}
\item It shall take steps to remedy student concerns regarding student life.
\begin{enumerate}
\item It shall advise the administration on issues related to student life, and work with them in addressing these issues.
\item It shall work and collaborate with the administration and other organizations to initiate new programs that improve the
student experience.
\end{enumerate}
\item It shall sustain and improve relations between the community at large and Rensselaer.
\begin{enumerate}
\item It shall provide students with opportunities to interact with the Troy community.
\end{enumerate}
\end{enumerate}