\article{Committees}
\begin{enumerate}

    \item The Chair of each Student Senate standing committee except the Rules and Elections Committee shall be nominated by the Grand Marshal and confirmed by a majority vote.
    \begin{enumerate}
        \item A Vice Chair may be selected by the Chair to assist in management and communication for the committee.

        \item For each committee project or initiative, a Project Lead shall be selected by the committee's chair;
        \begin{enumerate}
            \item Each project lead may create and lead a student task force, at the counsel of the committee's chair, to handle initiatives in their area requiring significant effort;

            \item The committee's chair shall assume the duties of any unfilled project lead position; and

            \item Project leads shall serve at the pleasure of the committee's chair.
        \end{enumerate}
    \end{enumerate}

    \item Committee membership shall be open to all members of the Rensselaer Union.
    \begin{enumerate}
        \item Any committee member who is not a member of the Senate must be approved by the Committee Chair before receiving
        membership in the committee.

        \item Members of a Committee serve at the pleasure of the Committee Chair and of the Grand Marshal, and may be removed at
        any time for good cause.

        \item Good cause for removal includes, but is not limited to, neglecting the duties of membership, failure to adhere to the the committee's rules of order during meetings if applicable, or failure to adhere to these Bylaws when conducting business in the name of the committee.
        \begin{enumerate}
            \item Members are expected to dutifully attend meetings of the committee and complete committee assignments within reasonable deadlines.
        \end{enumerate}
    \end{enumerate}

    \item All committees shall be empowered to create subcommittees as necessary to aid them in performing their functions, and subcommittees shall stand at the pleasure of the committee's chair. The committee's chair shall be an ex-officio member of any such created or existing subcommittee.

    \item All committees shall meet at least twice per month during regular academic periods to work on projects, investigate pending legislation, and to consider proposals for new legislation. Attendance shall be recorded at all committee meetings and submitted to the Grand Marshal. All committee chairs shall report on any open projects within their committees' purview at each Senate meeting.

    \item Each committee chair shall be held accountable for their committee's performance.

    \item During meetings, each Committee shall follow rules of order determined at the discretion of its Chair.

    \input{Articles/Committees/rne.tex}

    \input{Articles/Committees/sgcc.tex}

    \input{Articles/Committees/aac.tex}

    \input{Articles/Committees/uar.tex}

    \input{Articles/Committees/fsc.tex}

    \input{Articles/Committees/hsac.tex}

    \input{Articles/Committees/slc.tex}

    \input{Articles/Committees/wtg.tex}

    \input{Articles/Committees/crc.tex}

\end{enumerate}
