\article{Meetings}

\begin{enumerate}

    \item The Student Senate shall meet at least twice a month during normal academic periods. The time and location of these meetings shall be at the discretion of the Grand Marshal.

    \item All meetings of the Student Senate shall be open to the public.

    \item The Senate may, by a $\frac{2}{3}$ vote, close a meeting. Within a closed meeting the following guidelines must be met:
    \begin{enumerate}
        \item All motions, resolutions, and votes passed during the closed meeting must be made public immediately after the meeting is
        opened; and
        \item The Senate may invite non-Senate members to remain by a majority vote.
    \end{enumerate}

    \item The Senate may, by a majority vote, open a closed meeting.

    \item A quorum shall consist of $\frac{2}{3}$ of the voting membership of the Student Senate.

    \item The Student Senate shall use the current edition of Robert’s Rules of Order as their parliamentary authority for any procedures not specified in these Bylaws.

    \item The order of the agenda for a meeting of the Senate may be specified by the meeting’s presiding officer prior to the start of the meeting; if unspecified, the agenda order shall be set by what is specified in Robert’s Rules of Order.

    \item Meetings may be called by one-quarter of the voting membership of the Senate or by the Grand Marshal. The requesting
    Senators may name a Senator other than the Grand Marshal to preside over the meeting. The Grand Marshal must be notified of
    any meeting.
    \begin{enumerate}
        \item The presiding officer is responsible for informing all Senators at least twenty-four hours prior to the meeting as to the date, time, place, and purpose of the meeting. Normal procedures for running this meeting must be followed.
    \end{enumerate}

\end{enumerate}
