\article{Officers}

\begin{enumerate}

\item The Grand Marshal is the presiding officer of the Senate.

\item \textbf{The Officers of the Senate shall be:
\begin{enumerate}
\item The chairs of any committee formed by these Bylaws or the Student Senate
\item The Vice Chair,
\item The Secretary,
\item The Treasurer,
\item The Parliamentarian, and
\item The Senate-Executive Board Liaison
\end{enumerate}}

\item All Officers of the Senate, with the exception of the Grand Marshal, shall be nominated by the Grand Marshal and confirmed
by a $\frac{2}{3}$ vote of the Senate.

\item \textbf{All Officers of the Senate, with the exception of the Grand Marshal and the Senate-Executive Board Liaison, shall serve at the pleasure of the Grand Marshal.}

\item The Grand Marshal assumes the duties of any unfilled officer position, with the exception of the Rules and Elections
Committee Chair.
\begin{enumerate}
\item \textbf{These duties can be delegated by the Grand Marshal as Interim Officer positions, subject to confirmation by a majority vote of the Senate.}
\end{enumerate}

\item \textbf{The Vice Chair shall be responsible for:
\begin{enumerate}
\item Publicizing meeting times;
\item Meeting regularly with the Grand Marshal to discuss Senate issues;
\item Acting as the substitute for the Grand Marshal at any meetings that the Grand Marshal cannot attend. At such a meeting, the Vice Chair shall not count towards quorum and may only vote to break a tie;
\item Becoming familiar with the work of all the Senate committees, and assist committees in their duties;
\item Assisting individual Senators that have been charged with investigating issues raised by petition; and
\item Coordinating annual documentation folders with committee chairs to ensure continuity between years.
\end{enumerate}}

\item \textbf{The Secretary shall be responsible for:
\begin{enumerate}
\item Taking meeting attendance and minutes;
\item Distributing minutes, committee reports, motions, and other printed material to the members of the Student Senate within 48 hours following the adjournment of the meeting; and
\item Maintaining a roster of current membership of the Senate, along with contact information for each member.
\end{enumerate}}

\item The Treasurer shall be responsible for:
\begin{enumerate}
\item Managing funds allocated to the Student Senate as directed by the Grand Marshal or the Student Senate;
\item Preparing the annual budget of the Student Senate, subject to the approval of the Grand Marshal; and
\item Approving transactions conducted by the Senate or any of its Committees. The Grand Marshal may overrule any decision
pertaining to such transactions.
\end{enumerate}

\item \textbf{The Parliamentarian shall be responsible for:
\begin{enumerate}
\item Advising the presiding officer on matters of parliamentary procedure;
\item Maintaining an orderly meeting, abiding by rules of decorum; and
\item Maintaining an accurate record of all legislation brought before the Senate.
\end{enumerate}}

\item \textbf{The Student Senate’s representative on the Rensselaer Union Executive Board, hereinafter referred to as the Executive Board, shall be known as the Senate-Executive Board Liaison. They shall be responsible for:
\begin{enumerate}
\item Expressing the Senate’s opinions to the Executive Board and the Executive Board’s opinions to the Senate; and
\item Reviewing all legislation pertinent to Union fiscal policy and student fees.
\end{enumerate}}

\item \textbf{The chair of any Senate committee may not necessarily be a voting member of the Senate, but shall regularly attend Senate meetings.}

\end{enumerate}
