\article{Succession}
\begin{enumerate}
\item If the Grand Marshal is removed from office, has an extended leave of absence, or is otherwise unable to fulfill the duties or
requirements of office, then the Vice Chair shall assume the duties of the Grand Marshal as Acting Chair of the Senate.
\item The Acting Chair of the Senate assumes the duties of Grand Marshal until such a time that a meeting of the Senate can be
called. The first and only order of business of such a meeting shall be the selection of a new Grand Marshal.
\item All nominations for the position of Grand Marshal must be motioned and seconded by the members of the Senate. The
nomination processes shall be overseen by the Chair of the Judicial Board.
\begin{enumerate}
\item All nominees must be Senators as defined in these Bylaws.
\end{enumerate}
\item In the case of multiple nominees, an appointment for Grand Marshal shall be selected by a series of simple majority votes.
\begin{enumerate}
\item If there are two nominees, a vote shall be taken, and the nominee with a simple majority shall be named the appointment
for Grand Marshal.
\item If there are three or more nominees, a series of votes shall be taken. 
\begin{enumerate}
\item In each vote, the nominee with the least number of votes shall be removed from consideration, and only the remaining
nominees shall be considered in the next vote.
\item This series of votes shall continue until a single nominee remains, and that nominee shall be named the appointment for
Grand Marshal.
\end{enumerate}
\end{enumerate}

\item The nominee who is named the appointment for Grand Marshal must be approved by $\frac{2}{3}$ of the Senate’s total voting
membership. If the appointment is not approved, a new process of nominations begins.
\item Once a new Grand Marshal has been named, the Acting Chair of the Senate shall relinquish the responsibilities of office to the
new Grand Marshal.
\item The new Grand Marshal may appoint new officers of the Senate and committee chairs.

\end{enumerate}